Condition-Based Maintenance for Systems based on Bayesian Component Models***

### 2016-09-29 cbm-rbd-paper.tex
adding refs file

***to add timing of next inspection into the model we would need to add interval-censored data
(failure has happened between last and current inspection)

***3-param Weibull for repaired/exchanged components? Means `just' to shift time?
(introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as `unshifted' component type)

***Wang \& Jia 2007 give a model that uses Bayesian updating,
but the actual model is different:

They have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
The expected overall cost rate is then used to find a cost-optimal inspection interval.
For this they assume that failures are immediately repaired,
and defects found in an inspection are then repaired.
Is this really CBM?

@@

We do not assume a parametric distribution for delay time,
it rather arises as a consequence of the system layout and component failure distributions.

Our model gives the lower and upper delay time distribution at $\tnow$,
so takes current system condition into account.
We need additional criteria to indicate repair now yes/no.
(Could indicate which failed component(s) to repair best.)

@@

%\bibliographystyle{elsarticle-num}
%\bibliography{refs}

>>>>

Our model gives the lower and upper delay time distribution at $\tnow$,
so takes current system condition into account.

We need additional criteria to indicate repair now yes/no.
(Could indicate which failed component(s) to repair best.)

\subsection{Literature***}

example for Bayesian method in maintenance planning: \cite{2007:wang-jia}

***Wang \& Jia (2007) propose a model that uses Bayesian updating,
but the model aims to identify an optimal inspection interval.
This is CBM via inspections, not CBM via continuous monitoring as we aim to do.

Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
The expected overall cost rate is then used to find a cost-optimal inspection interval.
For this they assume that failures are immediately repaired,
and defects found in an inspection are repaired during inspection.

@@

(We do not assume a parametric distribution for delay time,
it rather arises as a consequence of the system layout and component failure distributions.)

\section{Outlook}

*** to add timing of next inspection into the model we would need to add interval-censored data
(failure has happened between last and current inspection)

*** if repaired/exchanged components are present in system,
the one needs to use actual ages (and not time since system startup) in parameter update,
introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type

@@

\bibliographystyle{elsarticle-harv}
\bibliography{refs}
